---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Load the package
```{r setup}
library(MLR)
```

Using the R built-in dataset `mtcars` to illustrate how to use the package `MLR` to conduct multiple linear regression.

## Fit the linear model
### Load the dataset
```{r}
data = mtcars
head(mtcars)
```
The main function in the package `MLR` is `mlr`. 

The output is a list of analytical results, which containing the following seven objects:

* `y.fitted:`: the fitted values of the model, as a vector
* `y.res`: the residuals of the model, as a vector
* `summary`: the estimated coefficients, as a table, which also contains the results of a two-sided t-test
* `FP`: F statistic and p value
* `vcov.matrix`: the variance-covariance matrix
* `ANOVA.table`: the results of an ANOVA test, as a list
* `R_Square`: the R-squared and adjusted R-square, as a vector of length 2


```{r}
model1 <- mlr("mpg", c("wt","hp","vs"), data=mtcars)
 
```

Get the fitted values and residuals of the model
```{r}
model1$y.fitted
model1$y.res
```

Get the estimated coefficients and the F statistic and also R Squared
```{r}
model1$summary
model1$FP
model1$R_Square
```

Get the the variance-covariance matrix
```{r}
model1$vcov.matrix
```

Get the anova table
```{r}
model1$ANOVA.table
```

The second function in the package 'MLR' is 'Cov_selected'.

Select covariates using the significance level(If not provided, 0.05 is used)

```{r}
# Cov_selected(model1)
```
In this model, variable 'wt' and 'hp' are selected.

## Compare results to base functions

```{r}
# test
form2 <- mpg ~ wt + hp +vs
model2 <- lm(formula = form2, data = mtcars)
model2_sum <- summary(model2)
model2_anova <- anova(model2)
```


```{r}
# y fitted values
#fitted_values_m2 <- matrix(unlist(model2$fitted.values), nrow = 1, byrow = TRUE)
fitted_values_m2 <-as.matrix(model2$fitted.values)
all.equal(model1$y.fitted, fitted_values_m2, check.attributes = F)

# Check residuals
#residuals_m2 <- matrix(unlist(model2$residuals), nrow = 1, byrow = TRUE)
residuals_m2 <- as.matrix(model2$residuals)
all.equal(model1$y.res,residuals_m2, check.attributes = F)

#Check coefficents
all.equal(model1$summary, model2_sum$coefficients, check.attributes = F)

# Check F test
all.equal(model1$FP[[1]], model2_sum$fstatistic["value"], check.attributes = F)

# variance matrix
all.equal(model1$vcov.matrix, vcov(model2), check.attributes = F)

#Check anova(seperate by column)
all.equal(model1$ANOVA.table,as.matrix(model2_anova), check.attributes = F)

#Check R squared
all.equal(model1$R_Square, c(model2_sum$r.squared,model2_sum$adj.r.squared), check.attributes = F)

```
All the results are true which shows that this is a correct function.

One advantage of `mlr()`, is that we can access important model components without needing to use additional functions like `summary()` or `vcov()`, it is very convenient.


## Compare speed to base functions
When we compare the efficiency of `mlr()` to `lm()` using the **bench** package, the output tables below show that their speeds are similar, sometimes `mlr()` is even faster.

compare the R squared value
```{r }
bench::mark(
  mlr("mpg", c("wt","hp","vs"), data=mtcars)$R_Square[[1]],
  summary(lm(form2, mtcars))$r.squared
)

```

compare variance and covariance matrix
```{r compare}
bench::mark(
  mlr("mpg", c("wt","hp","vs"), data=mtcars)$vcov.matrix,
  vcov(lm(form2, mtcars))
)
```

